Verifying Demonstrations

### 2017-10-04 protocol.tex
Adds sketch of protocol diagram
This diagram should be rewritten using a nice protocol diagram package.

  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    Structure of a proof share.
    The protester's identifier \(pid\) is computed using the protester's key 
    \(k_p\).
    The witness's identifier \(wid\) is computed using the witness's key 
    \(k_w\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
  }}%
  \label{fig:ProofFig}
\end{figure}
\end{frame}

\begin{figure}
  \centering
  \dots
  \caption{%
    An overview of message exchanges.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

>>>>

  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
  }}%
  \label{fig:ProofFig}
\end{figure}%
\end{frame}

\begin{frame}
\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & pid\gets PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\colon & wid\gets PRF_{k_W}(pid), \\
        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig) \\
      P\to S\colon & (pid, wid, t_s, l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}
\end{frame}
